quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-13 paper-quollr.Rmd
Added high-d model vis

Displaying the $p\text{-}D$ model overlaid on the data is done using the function `show_langevitour()`. This visualization is helpful for visually evaluating how well the model fits the data. The function requires several arguments: data along with their corresponding hexagonal bin ID, $2\text{-}D$ and $p\text{-}D$ model points, the threshold for removing long edges, and the distance data set.

@@

>>>>

To evaluate how well the $p\text{-}D$ model captures the underlying structure of the high-dimensional data, we provide a visualization using the `show_langevitour()` function. This function renders a dynamic projection of both the high-dimensional data and the model using the `langevitour` package.

Before plotting, the data needs to be organized into a combined format through the `comb_data_model()` function. This function takes three inputs: `highd_data` (the high-dimensional observations), `model_highd` (high-dimensional summaries for each bin), and `model_2d` (the hexagonal bin centroids of the model). It returns a tidy data frame combining both the data and the model.

In this structure, the `type` variable distinguishes between original observations (`"data"`) and the bin-averaged model representation (`"model"`).

@@

The `show_langevitour()` function then renders the visualization using the `langevitour` interface, displaying both types of points in a dynamic tour. The `edge_data` input defines connections between neighboring bins (i.e., the hexagonal edges) to visualize the model’s structure.

In the resulting interactive visualization black points represent the high-dimensional data, green points represent the model centroids from each bin, and the lines between model points reflect the $2-\text{D}$ wireframe structure mapped back to high-dimensional space.

### 2025-05-13 paper-quollr.tex
Added high-d model vis

Displaying the \(p\text{-}D\) model overlaid on the data is done using the function \texttt{show\_langevitour()}. This visualization is helpful for visually evaluating how well the model fits the data. The function requires several arguments: data along with their corresponding hexagonal bin ID, \(2\text{-}D\) and \(p\text{-}D\) model points, the threshold for removing long edges, and the distance data set.

@@

>>>>

To evaluate how well the \(p\text{-}D\) model captures the underlying structure of the high-dimensional data, we provide a visualization using the \texttt{show\_langevitour()} function. This function renders a dynamic projection of both the high-dimensional data and the model using the \texttt{langevitour} package.

Before plotting, the data needs to be organized into a combined format through the \texttt{comb\_data\_model()} function. This function takes three inputs: \texttt{highd\_data} (the high-dimensional observations), \texttt{model\_highd} (high-dimensional summaries for each bin), and \texttt{model\_2d} (the hexagonal bin centroids of the model). It returns a tidy data frame combining both the data and the model.

In this structure, the \texttt{type} variable distinguishes between original observations (\texttt{"data"}) and the bin-averaged model representation (\texttt{"model"}).

@@

The \texttt{show\_langevitour()} function then renders the visualization using the \texttt{langevitour} interface, displaying both types of points in a dynamic tour. The \texttt{edge\_data} input defines connections between neighboring bins (i.e., the hexagonal edges) to visualize the model's structure.

In the resulting interactive visualization black points represent the high-dimensional data, green points represent the model centroids from each bin, and the lines between model points reflect the \(2-\text{D}\) wireframe structure mapped back to high-dimensional space.
